Study protocol

### 2022-02-01 Manuscript/S1.Protocol.Rmd
style up

knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	eval = FALSE,
	dpi = 400,
	fig.pos = "H", out.extra = ""
)

```

@@

source('R/Setup.R') # Load the framework

@@

# Year filter. The framework converts it to the API-specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- '2010-2020'

```

@@

```{r secrets}
options(baysren.ieee_api_key = 'your-ieee-api-key')
options(baysren.ncbi_api_key = 'your-ncbi-api-key')
options(baysren.wos_api_key = 'your-wos-api-key')
```

@@

journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

```

@@

```{r managing records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%

	# Read record files. Will parse them if raw data is downloaded manually (not
	# necessary in this case). Return a list of records, one per file.
	read_bib_files() %>%

	# Join a list of records into one dataframe, solving duplicated records
	join_records() %>%

	# Order records by the relative frequency of the query terms in the title +
	# abstract text. Increases the chance of encountering relevant records at the
	# beginning of the manual classification.
	order_by_query_match(query) %>%

	# Add fields for the manual classification
	mutate(
			Rev_manual = NA, # Where the first manual classification will be made
			Rev_prediction = NA, # Column for the evaluation of the predicted classes
			.before = DOI
		)

```

@@

	# or specific record file folders
input <- file.path('Records', 'Session1', 'Query1')

	# or parent folders, since it searches for files recursively
input <- 'Records'

@@

# We can then call create_annotation_file() with one of the above input
Annotation_data <- create_annotation_file(input, reorder_query = query)

```

@@

```{r create session}
# Create the first session
create_session(Annotation_data, session_name = 'Session1')
```

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	journal = 'Session_journal.csv') %>%

	# return the record file paths
	extract_source_file_paths() %>%

	# read, join, reorder records and save them in the Sessions folder
	create_annotation_file(reorder_query = query) %>%

	# Create a new session with the records
	create_session(session_name = 'Session1')
```

@@

```{r automatic annotation}
New_annotations <- enrich_annotation_file('Session1')
```

@@

candidate_queries <- extract_rules('Session1')

@@

# No default is given for the save file, since generate_rule_selection_set()
# have no info about the session it's working on.
selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')

selection_set <- generate_rule_selection_set(
	candidate_queries$rule,
	target_vec = Target,
	target_data = SpecificDTM,
	save_path = selection_set_file)

@@

simplified_rules <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx') %>%
	import_data() %>%
	simplify_ruleset(target_vec = Target, target_data = SpecificDTM) %>%
	pull(rule)

@@

new_query <- rules_to_query(simplified_rules)

```

@@

```{r second session query}
query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase NOT
(patient transport) NOT (control infection use)) OR ((patient transport) NOT
(Donker T) NOT worker) OR (hospitals AND (network patient) NOT
(patient transport) NOT regional NOT clinical) OR (facility AND
(network patient) NOT hospitals NOT (patient transport) NOT regional NOT
prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT
hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))"

```

@@

# Repeat the search with the new query, giving a different Session name not to
# override previous records
journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session2', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

# Get the path to the annotated data in the previous session
previousAnnotations <- get_session_files('Session1')$Annotations %>% last()

# Create the new annotation file passing the folder with the new records
Annotation_data <- create_annotation_file(
	file.path('Records', 'Session2'),
	reorder_query = query,
	prev_records = previousAnnotations
)

# Create the new annotation session
create_session(Annotation_data, session_name = "Session2")

```

@@

```{r grid search}
Grid_search <- perform_grid_evaluation(
	records, sessions_folder = 'Grid_Search',
	prev_classification = records,
	## Model parameters (can be changed by users)
	resample = c(FALSE, TRUE),
	n_init = c(50, 100, 250, 500),
	n_models = c(1, 5, 10, 20, 40, 60),
	pos_mult = c(1, 10, 20),
	pred_quants = list(
		c(.1, .5, .9),
		c(.05, .5, .95),
		c(.01, .5, .99))
)
```

>>>>

knitr::opts_chunk$set(
  echo = TRUE,
  error = FALSE,
  message = FALSE,
  warning = FALSE,
  include = TRUE,
  eval = FALSE,
  dpi = 400,
  fig.pos = "H", out.extra = ""
)
```

@@

source("R/Setup.R") # Load the framework

@@

# Year filter. The framework converts it to the API-specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- "2010-2020"
```

@@

```{r secrets}
options(baysren.ieee_api_key = "your-ieee-api-key")
options(baysren.ncbi_api_key = "your-ncbi-api-key")
options(baysren.wos_api_key = "your-wos-api-key")
```

@@

journal <- perform_search_session(
  query = query, year_query = year_filter,
  session_name = "Session1", query_name = "Query1",
  records_folder = "Records",
  journal = "Session_journal.csv"
)
```

@@

```{r managing records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%
  # Read record files. Will parse them if raw data is downloaded manually (not
  # necessary in this case). Return a list of records, one per file.
  read_bib_files() %>%
  # Join a list of records into one dataframe, solving duplicated records
  join_records() %>%
  # Order records by the relative frequency of the query terms in the title +
  # abstract text. Increases the chance of encountering relevant records at the
  # beginning of the manual classification.
  order_by_query_match(query) %>%
  # Add fields for the manual classification
  mutate(
    Rev_manual = NA, # Where the first manual classification will be made
    Rev_prediction = NA, # Column for the evaluation of the predicted classes
    .before = DOI
  )
```

@@

# or specific record file folders
input <- file.path("Records", "Session1", "Query1")

# or parent folders, since it searches for files recursively
input <- "Records"

@@

# We can then call create_annotation_file() with one of the above input
Annotation_data <- create_annotation_file(input, reorder_query = query)
```

@@

```{r create session}
# Create the first session
create_session(Annotation_data, session_name = "Session1")
```

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(
  query = query, year_query = year_filter,
  session_name = "Session1", query_name = "Query1",
  journal = "Session_journal.csv"
) %>%
  # return the record file paths
  extract_source_file_paths() %>%
  # read, join, reorder records and save them in the Sessions folder
  create_annotation_file(reorder_query = query) %>%
  # Create a new session with the records
  create_session(session_name = "Session1")
```

@@

```{r automatic annotation}
New_annotations <- enrich_annotation_file("Session1")
```

@@

candidate_queries <- extract_rules("Session1")

@@

# No default is given for the save file, since generate_rule_selection_set()
# have no info about the session it's working on.
selection_set_file <- file.path("Sessions", "Session1", "Selected_rules.xlsx")

selection_set <- generate_rule_selection_set(
  candidate_queries$rule,
  target_vec = Target,
  target_data = SpecificDTM,
  save_path = selection_set_file
)

@@

simplified_rules <- file.path("Sessions", "Session1", "Selected_rules.xlsx") %>%
  import_data() %>%
  simplify_ruleset(target_vec = Target, target_data = SpecificDTM) %>%
  pull(rule)

@@

new_query <- rules_to_query(simplified_rules)
```

@@

```{r second session query}
query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase NOT
(patient transport) NOT (control infection use)) OR ((patient transport) NOT
(Donker T) NOT worker) OR (hospitals AND (network patient) NOT
(patient transport) NOT regional NOT clinical) OR (facility AND
(network patient) NOT hospitals NOT (patient transport) NOT regional NOT
prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT
hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))"
```

@@

# Repeat the search with the new query, giving a different Session name not to
# override previous records
journal <- perform_search_session(
  query = query, year_query = year_filter,
  session_name = "Session2", query_name = "Query1",
  records_folder = "Records",
  journal = "Session_journal.csv"
)

# Get the path to the annotated data in the previous session
previousAnnotations <- get_session_files("Session1")$Annotations %>% last()

# Create the new annotation file passing the folder with the new records
Annotation_data <- create_annotation_file(
  file.path("Records", "Session2"),
  reorder_query = query,
  prev_records = previousAnnotations
)

# Create the new annotation session
create_session(Annotation_data, session_name = "Session2")
```

@@

```{r grid search}
Grid_search <- perform_grid_evaluation(
  records,
  sessions_folder = "Grid_Search",
  prev_classification = records,
  ## Model parameters (can be changed by users)
  resample = c(FALSE, TRUE),
  n_init = c(50, 100, 250, 500),
  n_models = c(1, 5, 10, 20, 40, 60),
  pos_mult = c(1, 10, 20),
  pred_quants = list(
    c(.1, .5, .9),
    c(.05, .5, .95),
    c(.01, .5, .99)
  )
)
```
